---
title: ""
output: html_document
bibliography: bibliographies/DSethics-summer2023.bib
link-citations: true
csl: bibliographies/apa-6th-edition.csl
---

:::: column-page
# Most Common Syllabi Topics

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(reactable)
library(reactablefmtr)
```

::: {.callout-note icon="false" collapse="false"}
### Collation Methodology

To determine the syllabi topics, we took the listed course topics, available on [the data science ethics syllabi page](inside-syllabi.qmd), and collated them on one spreadsheet. We then grouped the course topics under more general headings (e.g., we put the 'Labor, Automation, and Regulation' under the heading of 'Workplace') to create a more concise list of the syllabi topics.

-   Link to [syllabi-topics.csv](https://github.com/scolando/DSethics-summer2023/blob/main/Rmds/syllabi-topics.csv)
:::

------------------------------------------------------------------------

# All Syllabi Topics

------------------------------------------------------------------------

```{r}
#| message: FALSE
#| warning: FALSE
#| fig.alt: "This is a table of the syllabi topics ordered from most common to least common. There are two columns: 'Syllabi Topic' and 'Count'. 'Count' represents the number of times the syllabi topic came up in the collected syllabi. The most common topic is 'Privacy' with a count of 11. 'Privacy' is followed by 'Bias' and 'Justice', both of which a count of 8."
#| fig.align: 'center'
#| fig.cap: "All syllabi topics, arranged in descending order by count."
#| label: fig-all-syallbi-topics
syllabi_topics <- readr::read_csv("syllabi-topics.csv")

syllabi_topics %>%
  group_by(Syllabi_Topics) %>%
  count() %>%
  arrange(desc(n)) %>%
  rename(Count = n) %>%
  reactable(
    columns = list(Syllabi_Topics = colDef("Syllabi Topic"),
    Count = colDef("Count")),
    highlight = TRUE,
    showSortable = TRUE,
    showPagination = TRUE,
    searchable = TRUE,
    defaultPageSize = 8,
    width = '100%',
    theme = reactableTheme( highlightColor = "#FAF9F0", rowHighlightStyle = list(`border-left` = "0.15em solid #f0ba55;"), style = list( fontFamily = "Helvetica Neue", fontSize = '0.875em')))
```

------------------------------------------------------------------------

# Most Common Syllabi Topics

------------------------------------------------------------------------

[**'Most Common' = has a count of 3 or more**]{style="color:#364f7a; background-color: #f2f8fc; border: 0.15em solid #f2f8fc; border-radius: 4px;"} <br>

```{r}
#| message: FALSE
#| warning: FALSE
#| fig.align: 'center'
#| fig.alt: "This is a table of the most common syllabi topics ordered from most common to least common. There are two columns: 'Syllabi Topic' and 'Count'. 'Count' represents the number of times the syllabi topic came up in the collected syllabi. Only syllabi topics with a count greater or equal to 3 are in the table. The most common topic is 'Privacy' with a count of 11. 'Privacy' is followed by 'Bias' and 'Justice', both of which a count of 8."
#| fig.cap: "Most common syllabi topics, arranged in descending order by count."
#| label: fig-common-syllabi-topics
syllabi_topics <- readr::read_csv("syllabi-topics.csv")

syllabi_topics %>%
  group_by(Syllabi_Topics) %>%
  count() %>%
  arrange(desc(n)) %>%
  rename(Count = n) %>%
  filter(Count >= 3) %>% 
  reactable(
    columns = list(Syllabi_Topics = colDef("Syllabi Topic"),
    Count = colDef("Count")),
    highlight = TRUE,
    showSortable = TRUE,
    pagination = FALSE,
    searchable = TRUE,
    width = '100%',
    theme = reactableTheme( highlightColor = "#FAF9F0", rowHighlightStyle = list(`border-left` = "0.15em solid #f0ba55;"), style = list( fontFamily = "Helvetica Neue", fontSize = '0.875em')))
```
::::
